A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-22 crystal-gel/talk_Roscoff.tex
use the color scheme of iLM to differentiate the phases in pathsX. More friendly to color blind.

\begin{frame}{Dynamics: Bergeron > Ostwald}
	\vspace{\baselineskip}
	\begin{center}
	\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
	\end{center}
	\begin{columns}
	\column{0.5\textwidth}
	\begin{itemize}
	\item Individual trajectories
	\item Probability of path to X
	\end{itemize}
	\column{0.5\textwidth}
	\tikzsetnextfilename{pathsX2}%
	\begin{tikzpicture}
	\node[regular polygon, regular polygon sides=3, minimum width=5em] (tri){};
	\node[circle, minimum width=3.5em, fill=green!40, left=1em of tri.corner 2] (gas) {gas};
	\node[circle, minimum width=3.5em, draw, fill=white, right =1em of tri.corner 3] (liq) {liquid};
	\node[regular polygon, regular polygon sides=6, fill=red,minimum width=3.5em, inner sep=0, above=0 of tri.corner 1] (X) {crystal};
	\draw[->, very thick] ($(tri.corner 2)+(0,0.25em)$) -- ($(liq.west)+(0,0.25em)$) node[midway, above]{54\%}-- (X);
	\draw[->, very thick, dotted] ($(tri.corner 3)+(0,-0.25em)$) -- ($(gas.east)+(0,-0.25em)$) node[midway, below]{35\%}-- (X);
	\draw[->, very thick, dashed] (X) edge [in=190,out=-130,loop] node[left]{11\%} ();
	\end{tikzpicture}
	\end{columns}
\end{frame}

>>>>

\begin{frame}{Dynamics: Bergeron > Ostwald}
	\vspace{\baselineskip}
	\begin{center}
	\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
	\end{center}
	\begin{columns}
	\column{0.5\textwidth}
	\begin{itemize}
	\item Individual trajectories
	\item Probability of path to X
	\end{itemize}
	\column{0.5\textwidth}
	\tikzsetnextfilename{pathsX2}%
	\begin{tikzpicture}
		\colorlet{an}{black}
		\colorlet{gas}{ilmorange!50!-an}%
		\colorlet{crystal}{ilmcolor!50!-an}%
		\colorlet{liquid}{ilmcolor!90!-an}%
		\node[regular polygon, regular polygon sides=3, minimum width=5em] (tri){};
		\node[circle, minimum width=3.5em, fill=gas, left=1em of tri.corner 2] (gas) {gas};
		\node[circle, minimum width=3.5em, fill=liquid, right =1em of tri.corner 3] (liq) {liquid};
		\node[regular polygon, regular polygon sides=6, fill=crystal,minimum width=3.5em, inner sep=0, above=0 of tri.corner 1] (X) {crystal};
		\draw[->, very thick] ($(tri.corner 2)+(0,0.25em)$) -- ($(liq.west)+(0,0.25em)$) node[midway, above]{54\%}-- (X);
		\draw[->, very thick, dotted] ($(tri.corner 3)+(0,-0.25em)$) -- ($(gas.east)+(0,-0.25em)$) node[midway, below]{35\%}-- (X);
		\draw[->, very thick, dashed] (X) edge [in=190,out=-130,loop] node[left]{11\%} ();
	\end{tikzpicture}
	\end{columns}
\end{frame}
